Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
update section2

This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$). $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i}\xi_i^{\sum\limits_{\mathrm{x_i} = x_i} \mathrm{x_i}}$.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.

>>>>

This can be extended to Dirichlet distribution of $m$ dimensions $\dirichlet(\alphas)$ where $x$ take value from universe $\mathcal{X}$ of size $m$ (i.e., $\mathcal{X} = \{x_1, \cdots, x_m\}$). $\pi(\xis) = \dirichlet(\xis | \alphas) = \frac{\prod_{i = 1}^{m}\xi_i^{\alpha_i}}{B(\alphas)}$, and the likelihood for $Pr(x | \xis)$ is $\prod\limits_{\xi_i \in \xis}\xi_i^{\sum\limits_{\{\mathrm{x}_i|\mathrm{x}_i = x_i\}} \mathrm{x_i}}$.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
